Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-05-27 sports_analytics.Rmd
more win prob refs (will cite eventually)

>>>>

Some refs (cite later)

https://www.degruyter.com/document/doi/10.1515/jqas-2013-0100/html

https://www.taylorfrancis.com/chapters/edit/10.1201/9781315166070-14/situational-success-evaluating-decision-making-football-keith-goldner

http://stat.wharton.upenn.edu/~stjensen/papers/shanejensen.basketball2016.pdf

https://arxiv.org/pdf/2204.11777.pdf

https://content.iospress.com/download/journal-of-sports-analytics/jsa231?id=journal-of-sports-analytics%2Fjsa231

https://content.iospress.com/download/journal-of-sports-analytics/jsa279?id=journal-of-sports-analytics%2Fjsa279

https://content.iospress.com/articles/journal-of-sports-analytics/jsa190294?resultNumber=10&totalResults=1420&start=10&q=win+probability&resultsPageSize=10&rows=10#jsa-5-jsa190294-g009

https://www.degruyter.com/document/doi/10.1515/jqas-2019-0096/html

https://www.degruyter.com/document/doi/10.1515/jqas-2019-0089/html

https://www.degruyter.com/document/doi/10.1515/jqas-2019-0056/html

https://wires.onlinelibrary.wiley.com/doi/epdf/10.1002/wics.1358?saml_referrer

https://wires.onlinelibrary.wiley.com/doi/epdf/10.1002/wics.1483
